The DESC Tomographic 3x2pt Optimization challenge

### 2020-12-15 paper/paper.tex
adds minimal content

@@

\begin{abstract}
Here is the abstract.
\end{abstract}

@@

\accepted{June ??, 2020}
\submitjournal{the Astrophysical Journal Supplement}

@@

\section{Introduction}
\label{sec:intro}

>>>>

\newcommand{\placeholder}[1]{\textit{PLACEHOLDER: #1}}

@@

\begin{abstract}
The tomo challenge aims to compare methods for assigning photometrically observed galaxies to bins for a tomographic 3x2pt cosmological analysis, especially in cases where only restricted photometry can be used.
We present this challenge, and the results of different methods when applied to the problem.
\end{abstract}

@@

%\accepted{}
%\submitjournal{the Astrophysical Journal Supplement}

@@

\section{Introduction \& Motivation}

\begin{itemize}
    \item Lensing/clustering/3x2pt 
    \item Why bin galaxies for 3x2pt
    \item Current binning standards
    \item Constraints on potential binning methods
    \item Goal of challenge: identify binning method(s) leading to best cosmology constraints 
\end{itemize}

\url{https://arxiv.org/abs/1901.06495}

\url{https://arxiv.org/abs/astro-ph/0609338}

\section{Challenge Design}

\subsection{Philosophy}
\begin{itemize}
    \item Simplest challenge (optimistic data)
    \item Openness?
    \item Science-relevant metrics
    \item Performance at scale
\end{itemize}

\subsection{Data}

\begin{itemize}
    \item CosmoDC2 - description
    \item CosmoDC2 - discussion
    \item Noise properties
    \item Pre-selection 
    \item Metacal as a limitation
\end{itemize}

\subsection{Metrics}
\label{sec:metrics}

\begin{itemize}
    \item S/N of spectra, CCL
    \item DETF Figure of merit, FireCrown(?)
    \item mutual information
\end{itemize}

\placeholder{want to check performance at multiple stages of a cosmology analysis}

\subsection{Infrastructure}
\begin{itemize}
    \item Pull request submissions
    \item Data at NERSC
\end{itemize}

\subsection{Control Methods}
\begin{itemize}
    \item single bin
    \item one galaxy per bin?
    \item sanity check: random selection should be same as single bin
\end{itemize}

\section{Methods}
\begin{itemize}
    \item Gradient Boosting \@ jecampagne
    \item Neural Network \@EiffL
    \item Random Forest
    \item \placeholder{cuts in photometry space without redshift estimation \@barber?}
\end{itemize}

\section{Results}
\begin{itemize}
    \item Big table of results
    \item fisher matrix ellipses overplotted for top N methods
    \item Plots of n(z)
\end{itemize}

\section{Discussion}
\begin{itemize}
    \item Overall effectiveness of method classes
    \item Individual winner
    \item Largest number of bins that proves workable
\end{itemize}

\subsection{Future directions}

\begin{itemize}
    \item spectroscopic incompleteness
\end{itemize}

\section{Conclusions}
